Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 code/scenarios/cdsr/trunk/papers/AAAI2012/qsr-extraction.tex
qsr

For each object that Dora detects we compute 8 spatial relations between that object and each of the objects adjacent to it; adjacency is determined using a voronoi diagram, as is standard in geometric reasoning \cite{Forbus/etal2003}. The model used to compute these relations was inspired by the literature on modeling the semantics of spatial terms \cite{kelleher/costello:09,kelleher/vanGenabith:2006,regier/carlson:2001,gapp:1994}. The model accommodates both direction and distance as factors in the relative position of objects.

The relations we compute between each given \emph{landmark} object and its adjacent neighbours are analogous to the cardinal and intermediate points on the compass when the compass is centered on the object. The canonical directions of these relations are defined using the following vectors: $\langle0,1\rangle$, $\langle1,1\rangle$, $\langle1,0\rangle$, $\langle1,-1\rangle$, $\langle0,-1\rangle$, $\langle-1,-1\rangle$, $\langle-1,0\rangle$, $\langle-1,1\rangle$. The predicates used to denote these relations are named accordingly, e.g. \textit{xZeroYOne}, \textit{xOneYOne}, \textit{xOneYZero}, \textit{xOneYNegOne}, etc.

@@

% These spatial relationships between adjacent objects provide the structure necessary for analogical processing.

\begin{figure}
\centerline{
\includegraphics[width=\columnwidth]{./images/spatialRelations/xZeroYOne.png}
}
\caption{A visualisation of a the strength of a spatial relation across a region. In this figure the landmark is located at the center of the image and the direction vector used was $\langle0,1\rangle$ (i.e. above of the landmark). The lighter the pixel the stronger the spatial relation is deemed to be at that point.}
\label{fig:spr}
\end{figure}

\from{Nick}{TODO: Generating QSRs is this way allows us to\dots}

>>>>

For each object that Dora detects we compute the strengths of 8 spatial relations between that object and each of the objects adjacent to it; adjacency is determined using a voronoi diagram, as is standard in geometric reasoning \cite{Forbus/etal2003}. The strength of a computed relation for a given pair of objects represents the applicability of that relation to the pair.  Strength ranges from 0 to 1, with 0 being unsuitable. The model used to compute these relations was inspired by the literature on modeling the semantics of spatial terms \cite{kelleher/costello:09,kelleher/vanGenabith:2006,regier/carlson:2001,gapp:1994}. The model accommodates both direction and distance as factors in the relative position of objects.

The relations we compute between each given \emph{landmark} object and its adjacent neighbours are analogous to the cardinal and intermediate points on the compass when the compass is centered on the object. The canonical directions of these relations are defined using the following vectors: $\langle0,1\rangle$, $\langle1,1\rangle$, $\langle1,0\rangle$, $\langle1,-1\rangle$, $\langle0,-1\rangle$, $\langle-1,-1\rangle$, $\langle-1,0\rangle$, $\langle-1,1\rangle$. The predicates used to denote these relations are named accordingly, e.g. \textit{xZeroYPlus}, \textit{xPlusYPlus}, \textit{xPlusYZero}, \textit{xPlusYMinus}, etc.

@@

These spatial relationships between adjacent objects provide the structure necessary for analogical processing. Generating the relationships in this way (as opposed to, for example, simple coordinate-based thresholding) has the advantage that the presence and absence of relationships is represented on a continuous scale. This provides our representations with the flexibility necessary to manage the variation in perceptual information (i.e. the position of walls and objects) inevitable in human environments and robot perception.

In addition to spatial relations, we also create \emph{grouping entities}
from the robot sensor data. Grouping entities collect together sets of adjacent objects of the same type. For example, a classroom would likely have a group entity created in which all of the students' desks were members.

\begin{figure}
\centerline{
\includegraphics[width=\columnwidth]{./images/spatialRelations/xZeroYOne.png}
}
\caption{A visualisation of a the strength of a spatial relation across a region. The landmark is the red square and the direction vector used was $\langle0,1\rangle$ (i.e. above of the landmark). The lighter the pixel the stronger the spatial relation is deemed to be at that point.}
\label{fig:spr}
\end{figure}
